---
title: "Data Mining Homework1(Building_Permits.csv)"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  word_document: default
---


First, install some packages needed.
```{r include=FALSE}
library(Hmisc)
library(car)
library(dplyr)

```
Import the data and have a brief look.
```{r}
b_p=read.csv("Building_Permits.csv")
b_p[1:10,]
```
Now, we know the structure of the data.

Nominal attributes: Permit.Type, Street.Number, Street.Name, Street.Suffix, Current.Status, Existing.Use, Proposed.Use, Existing.Construction.Type, Proposed.Construction.Type, Zipcode,  Neighborhood...Analysis.Boundaries

Numeric attributes: Unit, Number.of.Existing.Stories, Number.of.Proposed.Stories, Estimated.Cost, Revised.Stories, Proposed.Units, Plansets, Supervisor.District

Then the summary can be done.

Divide the data set into two data.frame: p_nominal and p_numeric
```{r}
b_p_nominal<-select(b_p,Permit.Type, Street.Number, Street.Name, Street.Suffix, Current.Status, Existing.Use, Proposed.Use, Existing.Construction.Type, Proposed.Construction.Type, Zipcode, Plansets, Supervisor.District)


b_p_numeric<-select(b_p,Unit, Number.of.Existing.Stories, Number.of.Proposed.Stories, Estimated.Cost, Revised.Cost, Existing.Units, Proposed.Units)


```
Begin the summary.

```{r}
summary(b_p_numeric)
```
```{r}

b_p_nominal[["Permit.Type"]]<-as.factor(b_p_nominal[["Permit.Type"]])
b_p_nominal[["Street.Number"]]<-as.factor(b_p_nominal[["Street.Number"]])
b_p_nominal[["Existing.Construction.Type"]]<-as.factor(b_p_nominal[["Existing.Construction.Type"]])
b_p_nominal[["Proposed.Construction.Type"]]<-as.factor(b_p_nominal[["Proposed.Construction.Type"]])
b_p_nominal[["Zipcode"]]<-as.factor(b_p_nominal[["Zipcode"]])
b_p_nominal[["Plansets"]]<-as.factor(b_p_nominal[["Plansets"]])
b_p_nominal[["Supervisor.District"]]<-as.factor(b_p_nominal[["Supervisor.District"]])
summary(b_p_nominal)
```
Above we count the the top 5 items in each attribute. If this is not enough, the following script can count the frequency of all items once existed in a given attribute. The "x" stand for the name of the item, the "freq" is the frequency calculated. 
In addition, a bar plot is also given if some "visualization" is required.
```{r}
library(plyr)
library(Hmisc)
plyr::count(b_p[["Permit.Type"]])
b_p_permit_type_counts<-plyr::count(b_p[["Permit.Type"]])$freq
names(b_p_permit_type_counts)<-plyr::count(b_p[["Permit.Type"]])$x
barplot(b_p_permit_type_counts,main="Permit Type")
```
Visualization begins.
Visualize Unit.
From the QQ plot below, it is clearly the Unit does not fit the normal distribution.
```{r}
plyr::count(is.na(b_p[["Unit"]]))
hist(b_p[["Unit"]])
boxplot(b_p[["Unit"]])
summary(b_p[["Unit"]])
qqPlot(b_p[["Unit"]])
```


According to the summary above, we can get the position of data with in-normal units numbers, which include unit=0 and units more than 759.5(Q3+1.5IQR).
```{r}
b_p_unit_innormal<-dplyr::filter(b_p,Unit==0 | Unit>759.5)
summary(b_p_unit_innormal[["Unit"]])
```



Visualize "Number.of.Existing.Stories.
```{r}
summary(b_p[["Number.of.Existing.Stories"]])
hist(b_p[["Number.of.Existing.Stories"]])
boxplot(b_p[["Number.of.Existing.Stories"]])
qqPlot(b_p[["Number.of.Existing.Stories"]])
```
Visualize Number.of.Proposed.Stories.
```{r}
summary(b_p[["Number.of.Proposed.Stories"]])
hist(b_p[["Number.of.Proposed.Stories"]])
boxplot(b_p[["Number.of.Proposed.Stories"]])
qqPlot(b_p[["Number.of.Proposed.Stories"]])

```
Visualize Estimated.Cost.
```{r}
summary(b_p[["Estimated.Cost"]])
plyr::count(is.na(b_p[["Estimated.Cost"]])) #getting the number of data points except NA points.
hist(b_p[["Estimated.Cost"]])
boxplot(b_p[["Estimated.Cost"]])
qqPlot(b_p[["Estimated.Cost"]])
```
According to the summary and hist gram above, it's highly possible that some too big and too small values are incorrect.
So I decide to cut them off.
```{r}
b_p_estimated_cost_new<-dplyr::filter(b_p,Estimated.Cost<4e+05 & Estimated.Cost>100)
summary(b_p_estimated_cost_new[["Estimated.Cost"]])
plyr::count(is.na(b_p_estimated_cost_new[["Estimated.Cost"]])) #getting the number of data points after cutting possibly incorrect values.
hist(b_p_estimated_cost_new[["Estimated.Cost"]])
boxplot(b_p_estimated_cost_new[["Estimated.Cost"]])
qqPlot(b_p_estimated_cost_new[["Estimated.Cost"]])
```

Visualize Revised,Cost.
```{r}
summary(b_p[["Revised.Cost"]])
plyr::count(is.na(b_p[["Revised.Cost"]])) #getting the number of data points except NA points.
hist(b_p[["Revised.Cost"]])
boxplot(b_p[["Revised.Cost"]])
qqPlot(b_p[["Revised.Cost"]])
```
According to the summary and hist gram above, it's highly possible that some too big and too small values are incorrect.
So I decide to cut them off.
```{r}
b_p_revised_cost_new<-dplyr::filter(b_p,Revised.Cost>100 & Revised.Cost<4e+05)
summary(b_p_revised_cost_new[["Revised.Cost"]])
plyr::count(is.na(b_p_revised_cost_new[["Revised.Cost"]]))  #getting the number of data points after cutting possibly incorrect values.
hist(b_p_revised_cost_new[["Revised.Cost"]])
boxplot(b_p_revised_cost_new[["Revised.Cost"]])
qqPlot(b_p_revised_cost_new[["Revised.Cost"]])
```
Use the Revised.Cost to cover Existing.Cost, fill NAs in Revised.Cost with its Estimated.
In this way I come up with a list named "b_p_cost" and visualize it.
```{r}
b_p_cost<-b_p[["Revised.Cost"]]
b_p_cost[which(is.na(b_p_cost))]<-b_p[["Estimated.Cost"]][which(is.na(b_p_cost))]
summary(b_p_cost)
plyr::count(is.na(b_p_cost))
hist(b_p_cost)
boxplot(b_p_cost)
qqPlot(b_p_cost)
```
Using the same method cutting possible incorrect values and visualize it again.
```{r}
b_p_cost_new<-b_p_cost[which(b_p_cost>100 & b_p_cost<4e+05)]
summary(b_p_cost_new)
plyr::count(is.na(b_p_cost_new))  #getting the number of data points after cutting possibly incorrect values.
hist(b_p_cost_new)
boxplot(b_p_cost_new)
qqPlot(b_p_cost_new)
```



Visualize Existing.Units
```{r}

summary(b_p[["Existing.Units"]])
hist(b_p[["Existing.Units"]])
boxplot(b_p[["Existing.Units"]])
qqPlot(b_p[["Existing.Units"]])
```


Visualize Proposed.Units.
```{r}
summary(b_p[["Proposed.Units"]])
hist(b_p[["Proposed.Units"]])
boxplot(b_p[["Proposed.Units"]])
qqPlot(b_p[["Proposed.Units"]])
```



About missing data. 
First, list the missing data using mice package.
The blanks in column "Existing.Use" and "Proposed.Use" are filled with NA.
Then, focus on what we think is important, visualize the pattern of the missing data using VIM package.
```{r}
library(VIM)
library(lattice)
library(mice)
b_p_new<-cbind(b_p[["Permit.Number"]],b_p_nominal,b_p_numeric)
#md.pattern(b_p_new)
b_p_missing_visualize=dplyr::select(b_p,Existing.Use,Proposed.Use,Existing.Construction.Type,Proposed.Construction.Type,Unit,Number.of.Existing.Stories,Number.of.Proposed.Stories,Existing.Units,Proposed.Units,Plansets,Supervisor.District)
b_p_missing_visualize<-cbind(b_p_cost,b_p_missing_visualize)
b_p_missing_visualize[["Existing.Use"]][which( b_p_missing_visualize[["Existing.Use"]]=="")]<-NA
b_p_missing_visualize[["Proposed.Use"]][which( b_p_missing_visualize[["Proposed.Use"]]=="")]<-NA
#b_p_missing_visualize[["Revised.Cost"]][which( b_p_missing_visualize[["Revised.Cost"]]<50)]<-NA
aggr(b_p_missing_visualize, prop = TRUE, number = TRUE, combined = TRUE) 
```
```{r}
aggr(b_p_missing_visualize, prop = TRUE, number = TRUE, combined = FALSE) 
```

There are several theories for NA values.

Most NA values stands for things that never truly exist.
For example, as for the Permit.Type "new construction", the attribute Existing.Unit makes no sense. So NA is introduced to deal with this kind of situation.

Besides, equipment malfunction, data error or refusing of the person interviewed to provide data, things that that can also cause NA in original data set.



Dealing with missing data:omitting missing value.
This can be achieve using following script(take the Proposed.Units as an example).
It's obvious that this move does not change the visualization of a given attribute.
```{r}
summary(na.omit(b_p[["Proposed.Units"]]))
hist(na.omit(b_p[["Proposed.Units"]]))
```
Dealing with missing data: filling NA with value of largest frequency.
When dealing with nominal attributes, take "Proposed.Construction.Type" as an example.
```{r}
b_p_proposed_construction_type_new<-b_p[["Proposed.Construction.Type"]]
b_p_proposed_construction_type_new[is.na(b_p_proposed_construction_type_new)]<-plyr::count(b_p_proposed_construction_type_new)$x[which.max(plyr::count(b_p_proposed_construction_type_new)$freq)]
hist(b_p_proposed_construction_type_new,main="P.Con.Type after_filling")
hist(b_p[["Proposed.Construction.Type"]],main="P.Con.Type before_filling")
```
As for numeric attributes, the script below is used.
Unit
```{r}
b_p_unit_new<-b_p[["Unit"]]
temp=density(na.omit(b_p[["Unit"]]),bw=1)
b_p_unit_new[which(is.na(b_p_unit_new))]<-temp$x[which.max(temp$y)]
hist(b_p_unit_new,main="Unit after_filling")
hist(b_p[["Unit"]],main="Unit before_filling")
boxplot(b_p_unit_new,main="Unit after_filling")
boxplot(b_p[["Unit"]],main="Unit before_filling")
```
Number.of.Existing.Stories
```{r}
b_p_number_of_existing_stories_new<-b_p[["Number.of.Existing.Stories"]]
temp=density(na.omit(b_p[["Number.of.Existing.Stories"]]),bw=1)
b_p_number_of_existing_stories_new[which(is.na(b_p_number_of_existing_stories_new))]<-temp$x[which.max(temp$y)]
hist(b_p_number_of_existing_stories_new,main="N.of.Existing.S after_filling")
hist(b_p[["Number.of.Existing.Stories"]],main="N.of.Existing.S before_filling")
boxplot(b_p_number_of_existing_stories_new,main="N.of.Existing.S after_filling")
boxplot(b_p[["Number.of.Existing.Stories"]],main="N.of.Existing.S before_filling")
```

Number.of.Proposed.Stories
```{r}
b_p_number_of_proposed_stories_new<-b_p[["Number.of.Proposed.Stories"]]
temp=density(na.omit(b_p[["Number.of.Proposed.Stories"]]),bw=1)
b_p_number_of_proposed_stories_new[which(is.na(b_p[["Number.of.Proposed.Stories"]]))]<-temp$x[which.max(temp$y)]
hist(b_p_number_of_proposed_stories_new,main="N.of.Proposed.S after_filling")
hist(b_p[["Number.of.Proposed.Stories"]],main="N.of.Proposed.S before_filling")
boxplot(b_p_number_of_proposed_stories_new,main="N.of.Proposed.S after_filling")
boxplot(b_p[["Number.of.Proposed.Stories"]],main="N.of.Proposed.S before_filling")
```
Existing.Units
```{r}
b_p_existing_units_new<-b_p[["Existing.Units"]]
temp=density(na.omit(b_p[["Existing.Units"]]),bw=1)
b_p_existing_units_new[which(is.na(b_p_existing_units_new))]<-temp$x[which.max(temp$y)]
hist(b_p_existing_units_new,main="E.Units after_filling")
hist(b_p[["Existing.Units"]],main="E.Units before_filling")
boxplot(b_p_existing_units_new,main="E.Units after_filling")
boxplot(b_p[["Existing.Units"]],main="E.Units before_filling")
```

Proposed.Units
```{r}
b_p_proposed_units_new<-b_p[["Proposed.Units"]]
temp=density(na.omit(b_p[["Proposed.Units"]]),bw=1)
b_p_proposed_units_new[which(is.na(b_p_proposed_units_new))]<-temp$x[which.max(temp$y)]
hist(b_p_proposed_units_new,main="P.Units after_filling")
hist(b_p[["Proposed.Units"]],main="P.Units before_filling")
boxplot(b_p_proposed_units_new,main="P.Units after_filling")
boxplot(b_p[["Proposed.Units"]],main="P.Units before_filling")
```

b_p_cost
```{r}
b_p_cost_new<-b_p_cost
temp=density(na.omit(b_p_cost),bw=1)
b_p_cost_new[which(is.na(b_p_cost_new))]<-temp$x[which.max(temp$y)]
hist(b_p_cost_new,main="cost after_filling")
hist(b_p_cost,main="cost before_filling")
boxplot(b_p_cost_new,main="cost after_filling")
boxplot(b_p_cost,main="cost before_filling")
```

Before using some "advanced" method to fill NA values, we must have a closer look at the data set.
At first, we should know the number of types of permits and the features of each one.
```{r}
count(b_p[["Permit.Type"]])
```
Type1: new construction, "Existing.Units" and "Number.of.Existing.Units" should be NA, "Unit" should be 0.
Type2: new construction wood frame, "Units" and "Existing.Units" should be 0.
Type3: additional alterations or repairs, nothing special.
Type4: sign-erect, "Number.of.Proposed.Stories" and "Proposed.Units" should be 0.
Type5: grade or quarry or fill or excavate, "Number.of.Existing.Stories" and "Number.of.Proposed.Stories" should be NA, "Existing.Units", "Proposed.Units" and "Unit" should be 0.
Type6: demolitions, "Unit" should be 0, "Number.of.Proposed.Stories" and "Proposed.Units" should be NA.
Type7:wall or painted sign, "Number.of.Proposed.Stories" and "Proposed.Units" should be NA, "Existing.Units" should be 0.
Type8: otc alterations permits, nothing special.

Divide the numeric part of the data.frame by type.
```{r}
b_p_missing_numeric_with_type<-select(b_p,Permit.Type,Unit,Number.of.Existing.Stories,Number.of.Proposed.Stories,Existing.Units,Proposed.Units)
b_p_missing_numeric_with_type<-cbind(b_p_cost,b_p_missing_numeric_with_type)
b_p_numeric_type1<-b_p_missing_numeric_with_type[which(b_p_missing_numeric_with_type[["Permit.Type"]]==1),]
b_p_numeric_type2<-b_p_missing_numeric_with_type[which(b_p_missing_numeric_with_type[["Permit.Type"]]==2),]
b_p_numeric_type3<-b_p_missing_numeric_with_type[which(b_p_missing_numeric_with_type[["Permit.Type"]]==3),]
b_p_numeric_type4<-b_p_missing_numeric_with_type[which(b_p_missing_numeric_with_type[["Permit.Type"]]==4),]
b_p_numeric_type5<-b_p_missing_numeric_with_type[which(b_p_missing_numeric_with_type[["Permit.Type"]]==5),]
b_p_numeric_type6<-b_p_missing_numeric_with_type[which(b_p_missing_numeric_with_type[["Permit.Type"]]==6),]
b_p_numeric_type7<-b_p_missing_numeric_with_type[which(b_p_missing_numeric_with_type[["Permit.Type"]]==7),]
b_p_numeric_type8<-b_p_missing_numeric_with_type[which(b_p_missing_numeric_with_type[["Permit.Type"]]==8),]


```

Use correlation among attributes to fill NA values.
Package "mice" is introduced and it's used for imputing.
```{r}
library(mice)
```



Type 1
```{r}

symnum(cor(b_p_numeric_type1[,c(1,5,7)],use="complete.obs"))
```

There exist some data which all there meaningful attributes are missed. It's reasonably to discard them.
```{r}
library(DMwR)
b_p_numeric_type1_1<-b_p_numeric_type1[-manyNAs(b_p_numeric_type1[,c(1,5,7)],0.68),]
```


According to the correlation matrix, there is a strong linear relationship between b_p_cost and Number.of.Proposed.Stories as well as between b_p_cost and Proposed.Units.
So two linear models are fitted.

```{r}
lm(Number.of.Proposed.Stories~b_p_cost,data=b_p_numeric_type1_1)
lm(Proposed.Units~b_p_cost,data=b_p_numeric_type1_1)

```

Using the fitted models to fill NA values.
```{r}
b_p_numeric_type1_new<-b_p_numeric_type1_1
b_p_numeric_type1_new[which(is.na(b_p_numeric_type1_new[["Number.of.Proposed.Stories"]])),"Number.of.Proposed.Stories"]<-floor((9.293e-8)*b_p_numeric_type1_new[which(is.na(b_p_numeric_type1_new[["Number.of.Proposed.Stories"]])),"b_p_cost"]+5.07)

b_p_numeric_type1_new[which(is.na(b_p_numeric_type1_new[["Proposed.Units"]])),"Proposed.Units"]<-floor((1.17e-6)*b_p_numeric_type1_new[which(is.na(b_p_numeric_type1_new[["Proposed.Units"]])),"b_p_cost"]+49.59)

#b_p_numeric_type1_new<-select(b_p_numeric_type1_new,b_p_cost,Unit,Number.of.Existing.Stories,Number.of.Proposed.Stories,Existing.Units,Proposed.Units)
```













Type2
```{r}

symnum(cor(b_p_numeric_type2[,c(1,5,7)],use="complete.obs"))
```



```{r message=FALSE}
tempData_type2 <- mice( b_p_numeric_type2[,c(1,5,7)] ,m=3,maxit=10,meth="pmm")


```
```{r}
completedData <- complete(tempData_type2,1)
#completedData[["Unit"]]<-floor(completedData[["Units"]])
#completedData[["Number.of.Existing.Stories"]]<-floor(completedData[["Number.of.Existing.Stories"]])
completedData[["Number.of.Proposed.Stories"]]<-floor(completedData[["Number.of.Proposed.Stories"]])
#completedData[["Existing.Units"]]<-floor(completedData[["Existing.Units"]])
#completedData[["Proposed.Units"]]<-floor(completedData[["Proposed.Units"]])

b_p_numeric_type2_new<-b_p_numeric_type2
b_p_numeric_type2_new[,c(1,5,7)]<-completedData
summary(completedData)
```






Type3
```{r}

symnum(cor(b_p_numeric_type3[,c(1,3,4,5,6,7)],use="complete.obs"))
```


```{r message=FALSE}
tempData_type3 <- mice( b_p_numeric_type3[,c(1,3,4,5,6,7)] ,m=3,maxit=10,meth="pmm")


```
```{r}
completedData <- complete(tempData_type3,1)
#completedData[["Unit"]]<-floor(completedData[["Units"]])
completedData[["Number.of.Existing.Stories"]]<-floor(completedData[["Number.of.Existing.Stories"]])
completedData[["Number.of.Proposed.Stories"]]<-floor(completedData[["Number.of.Proposed.Stories"]])
completedData[["Existing.Units"]]<-floor(completedData[["Existing.Units"]])
completedData[["Proposed.Units"]]<-floor(completedData[["Proposed.Units"]])

b_p_numeric_type3_new<-b_p_numeric_type3
b_p_numeric_type3_new[,c(1,3,4,5,6,7)]<-completedData
summary(completedData)
```



Type4
```{r}

symnum(cor(b_p_numeric_type4[,c(1,3,4,6)],use="complete.obs"))
```
```{r message=FALSE}
tempData_type4 <- mice( b_p_numeric_type4[,c(1,3,4,6)] ,m=3,maxit=10,meth="pmm")


```

```{r}
completedData <- complete(tempData_type4,1)
#completedData[["Unit"]]<-floor(completedData[["Units"]])
completedData[["Number.of.Existing.Stories"]]<-floor(completedData[["Number.of.Existing.Stories"]])
#completedData[["Number.of.Proposed.Stories"]]<-floor(completedData[["Number.of.Proposed.Stories"]])
completedData[["Existing.Units"]]<-floor(completedData[["Existing.Units"]])
#completedData[["Proposed.Units"]]<-floor(completedData[["Proposed.Units"]])

b_p_numeric_type4_new<-b_p_numeric_type4
b_p_numeric_type4_new[,c(1,3,4,6)]<-completedData
summary(completedData)
```



Type5, as it is described before, its only meaningful attribute is the "b_p_cost".
```{r}
count(is.na(b_p_numeric_type5[["b_p_cost"]]))
```
Type5 does not need NA filling.
```{r}
b_p_numeric_type5_new<-b_p_numeric_type5
```



Type6
```{r}

symnum(cor(b_p_numeric_type6[,c(1,4,6)],use="complete.obs"))
```

```{r message=FALSE}
tempData_type6 <- mice( b_p_numeric_type6[,c(1,4,6)] ,m=3,maxit=10,meth="pmm")


```

```{r}
completedData <- complete(tempData_type6,1)
#completedData[["Unit"]]<-floor(completedData[["Units"]])
completedData[["Number.of.Existing.Stories"]]<-floor(completedData[["Number.of.Existing.Stories"]])
#completedData[["Number.of.Proposed.Stories"]]<-floor(completedData[["Number.of.Proposed.Stories"]])
completedData[["Existing.Units"]]<-floor(completedData[["Existing.Units"]])
#completedData[["Proposed.Units"]]<-floor(completedData[["Proposed.Units"]])

b_p_numeric_type6_new<-b_p_numeric_type6
b_p_numeric_type6_new[,c(1,4,6)]<-completedData
summary(completedData)
```



Type7
```{r}

symnum(cor(b_p_numeric_type7[,c(1,3)],use="complete.obs"))
```

```{r message=FALSE}
tempData_type7 <- mice( b_p_numeric_type7[,c(1,3)] ,m=3,maxit=10,meth="pmm")


```

```{r}
completedData <- complete(tempData_type7,1)
#completedData[["Unit"]]<-floor(completedData[["Units"]])
#completedData[["Number.of.Existing.Stories"]]<-floor(completedData[["Number.of.Existing.Stories"]])
#completedData[["Number.of.Proposed.Stories"]]<-floor(completedData[["Number.of.Proposed.Stories"]])
#completedData[["Existing.Units"]]<-floor(completedData[["Existing.Units"]])
#completedData[["Proposed.Units"]]<-floor(completedData[["Proposed.Units"]])

b_p_numeric_type7_new<-b_p_numeric_type7
b_p_numeric_type7_new[,c(1,3)]<-completedData
summary(completedData)
```



Type8
```{r}

symnum(cor(b_p_numeric_type8[,c(1,3,4,5,6,7)],use="complete.obs"))
```

```{r include=FALSE}
tempData_type8 <- mice( b_p_numeric_type8[,c(1,3,4,5,6,7)] ,m=1,maxit=2,meth="pmm")


```
```{r}
completedData <- complete(tempData_type8,1)
#completedData[["Unit"]]<-floor(completedData[["Units"]])
completedData[["Number.of.Existing.Stories"]]<-floor(completedData[["Number.of.Existing.Stories"]])
completedData[["Number.of.Proposed.Stories"]]<-floor(completedData[["Number.of.Proposed.Stories"]])
completedData[["Existing.Units"]]<-floor(completedData[["Existing.Units"]])
completedData[["Proposed.Units"]]<-floor(completedData[["Proposed.Units"]])

b_p_numeric_type8_new<-b_p_numeric_type8
b_p_numeric_type8_new[,c(1,3,4,5,6,7)]<-completedData
summary(completedData)
```

Combine those data and visualize it.
```{r}
b_p_missing_with_type_new<-rbind(b_p_numeric_type1_new[,1:7],b_p_numeric_type2_new,b_p_numeric_type3_new,b_p_numeric_type4_new,b_p_numeric_type5,b_p_numeric_type6_new,b_p_numeric_type7_new,b_p_numeric_type8_new)

hist(b_p_missing_with_type_new[["Unit"]])
hist(b_p_missing_with_type_new[["Number.of.Existing.Stories"]])
hist(b_p_missing_with_type_new[["Number.of.Proposed.Stories"]])
hist(b_p_missing_with_type_new[["Existing.Units"]])
hist(b_p_missing_with_type_new[["Proposed.Units"]])
hist(b_p_missing_with_type_new[["b_p_cost"]])

```
Box plot.
```{r}

boxplot(b_p_missing_with_type_new[["Unit"]])
boxplot(b_p_missing_with_type_new[["Number.of.Existing.Stories"]])
boxplot(b_p_missing_with_type_new[["Number.of.Proposed.Stories"]])
boxplot(b_p_missing_with_type_new[["Existing.Units"]])
boxplot(b_p_missing_with_type_new[["Proposed.Units"]])
boxplot(b_p_missing_with_type_new[["b_p_cost"]])
```









Deal with missing values by exploring exploring similarities among objects.

This method can be simply described as "The value of a given attribute of objects can be very close to each other if those objects are of the same type".

In this data, the type of each object is given. So a simply way using similarities of objects is filling NA with most frequent value of that type of objects.

The features of each type of permission are described above.

Type1
```{r}
b_p_numeric_type1_new2<-b_p_numeric_type1
b_p_numeric_type1_new2[which(is.na(b_p_numeric_type1_new[,1])),1]<-round(mean(b_p_numeric_type1[,1],na.rm = TRUE))
b_p_numeric_type1_new2[which(is.na(b_p_numeric_type1_new[,5])),5]<-round(mean(b_p_numeric_type1[,5],na.rm = TRUE))
b_p_numeric_type1_new2[which(is.na(b_p_numeric_type1_new[,7])),7]<-round(mean(b_p_numeric_type1[,7],na.rm = TRUE))
```


Type2
```{r}
b_p_numeric_type2_new2<-b_p_numeric_type2
b_p_numeric_type2_new2[which(is.na(b_p_numeric_type2_new[,1])),1]<-round(mean(b_p_numeric_type2[,1],na.rm = TRUE))
b_p_numeric_type2_new2[which(is.na(b_p_numeric_type2_new[,5])),5]<-round(mean(b_p_numeric_type2[,5],na.rm = TRUE))
b_p_numeric_type2_new2[which(is.na(b_p_numeric_type2_new[,7])),7]<-round(mean(b_p_numeric_type2[,7],na.rm = TRUE))
```

Type3
```{r}
b_p_numeric_type3_new2<-b_p_numeric_type3
b_p_numeric_type3_new2[which(is.na(b_p_numeric_type3_new[,1])),1]<-round(mean(b_p_numeric_type3[,1],na.rm = TRUE))
b_p_numeric_type3_new2[which(is.na(b_p_numeric_type3_new[,3])),3]<-round(mean(b_p_numeric_type3[,3],na.rm = TRUE))
b_p_numeric_type3_new2[which(is.na(b_p_numeric_type3_new[,4])),4]<-round(mean(b_p_numeric_type3[,4],na.rm = TRUE))
b_p_numeric_type3_new2[which(is.na(b_p_numeric_type3_new[,5])),5]<-round(mean(b_p_numeric_type3[,5],na.rm = TRUE))
b_p_numeric_type3_new2[which(is.na(b_p_numeric_type3_new[,6])),6]<-round(mean(b_p_numeric_type3[,6],na.rm = TRUE))
b_p_numeric_type3_new2[which(is.na(b_p_numeric_type3_new[,7])),7]<-round(mean(b_p_numeric_type3[,7],na.rm = TRUE))
```

Type4
```{r}
b_p_numeric_type4_new2<-b_p_numeric_type4
b_p_numeric_type4_new2[which(is.na(b_p_numeric_type4_new[,1])),1]<-round(mean(b_p_numeric_type4[,1],na.rm = TRUE))
b_p_numeric_type4_new2[which(is.na(b_p_numeric_type4_new[,3])),3]<-round(mean(b_p_numeric_type4[,3],na.rm = TRUE))
b_p_numeric_type4_new2[which(is.na(b_p_numeric_type4_new[,4])),4]<-round(mean(b_p_numeric_type4[,4],na.rm = TRUE))
b_p_numeric_type4_new2[which(is.na(b_p_numeric_type4_new[,6])),6]<-round(mean(b_p_numeric_type4[,6],na.rm = TRUE))
```

Type5
```{r}
b_p_numeric_type5_new2<-b_p_numeric_type5
```

Type6
```{r}
b_p_numeric_type6_new2<-b_p_numeric_type6
b_p_numeric_type6_new2[which(is.na(b_p_numeric_type6_new[,1])),1]<-round(mean(b_p_numeric_type6[,1],na.rm = TRUE))
b_p_numeric_type6_new2[which(is.na(b_p_numeric_type6_new[,3])),3]<-round(mean(b_p_numeric_type6[,3],na.rm = TRUE))
b_p_numeric_type6_new2[which(is.na(b_p_numeric_type6_new[,4])),4]<-round(mean(b_p_numeric_type6[,4],na.rm = TRUE))
b_p_numeric_type6_new2[which(is.na(b_p_numeric_type6_new[,6])),6]<-round(mean(b_p_numeric_type6[,6],na.rm = TRUE))
```


Type7
```{r}
b_p_numeric_type7_new2<-b_p_numeric_type7
b_p_numeric_type7_new2[which(is.na(b_p_numeric_type7_new[,1])),1]<-round(mean(b_p_numeric_type7[,1],na.rm = TRUE))
b_p_numeric_type7_new2[which(is.na(b_p_numeric_type7_new[,3])),3]<-round(mean(b_p_numeric_type7[,3],na.rm = TRUE))

```

Type8
```{r}
b_p_numeric_type8_new2<-b_p_numeric_type8
b_p_numeric_type8_new2[which(is.na(b_p_numeric_type8_new[,1])),1]<-round(mean(b_p_numeric_type8[,1],na.rm = TRUE))
b_p_numeric_type8_new2[which(is.na(b_p_numeric_type8_new[,3])),3]<-round(mean(b_p_numeric_type8[,3],na.rm = TRUE))
b_p_numeric_type8_new2[which(is.na(b_p_numeric_type8_new[,4])),4]<-round(mean(b_p_numeric_type8[,4],na.rm = TRUE))
b_p_numeric_type8_new2[which(is.na(b_p_numeric_type8_new[,5])),5]<-round(mean(b_p_numeric_type8[,5],na.rm = TRUE))
b_p_numeric_type8_new2[which(is.na(b_p_numeric_type8_new[,6])),6]<-round(mean(b_p_numeric_type8[,6],na.rm = TRUE))
b_p_numeric_type8_new2[which(is.na(b_p_numeric_type8_new[,7])),7]<-round(mean(b_p_numeric_type8[,7],na.rm = TRUE))
```

Combine those data and visualize it.
Hist plot.
```{r}
b_p_missing_with_type_new2<-rbind(b_p_numeric_type1_new2[,1:7],b_p_numeric_type2_new2,b_p_numeric_type3_new2,b_p_numeric_type4_new2,b_p_numeric_type5,b_p_numeric_type6_new2,b_p_numeric_type7_new2,b_p_numeric_type8_new2)

hist(b_p_missing_with_type_new2[["Unit"]])
hist(b_p_missing_with_type_new2[["Number.of.Existing.Stories"]])
hist(b_p_missing_with_type_new2[["Number.of.Proposed.Stories"]])
hist(b_p_missing_with_type_new2[["Existing.Units"]])
hist(b_p_missing_with_type_new2[["Proposed.Units"]])
hist(b_p_missing_with_type_new2[["b_p_cost"]])

```

Box plot.
```{r}

boxplot(b_p_missing_with_type_new2[["Unit"]])
boxplot(b_p_missing_with_type_new2[["Number.of.Existing.Stories"]])
boxplot(b_p_missing_with_type_new2[["Number.of.Proposed.Stories"]])
boxplot(b_p_missing_with_type_new2[["Existing.Units"]])
boxplot(b_p_missing_with_type_new2[["Proposed.Units"]])
boxplot(b_p_missing_with_type_new2[["b_p_cost"]])
```











