---
title: "Homework2-Frequent Itmesets Mining"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pre-procossing
  The Building_Permits data set is choosen for frequenct itemsets mining. Before the analysis, the dataset must be imported and changed to the suitable format.
   First, import the package "arules" which is the famous R package specilized in frequent itemsets mining. The package "arulesViz" is also needed for visualization of the rules found. The package "dplyr" which is very useful in data pre-processing is also imported.

```{r}
library(dplyr)
library(arules)
library(arulesViz)
```

```{r}
b_p<-read.csv("data_mining_homework/Building_Permits.csv")
```

  Extract the attributes needed for frequent itemsets mining, especially binary attributes.

```{r}
b_p_nominal<-select(b_p,"Permit.Type", "Street.Number", "Street.Name", "Street.Suffix", "Current.Status", "Existing.Use", "Proposed.Use", "Existing.Construction.Type", "Proposed.Construction.Type", "Zipcode", "Plansets", "Supervisor.District","Neighborhoods...Analysis.Boundaries")
```
  Convert the columns to factors and change the data.frame to a sparse matrix for further rearch.
```{r}
b_p_apriori<- b_p_nominal
for (i in 1:13) {
  b_p_apriori[[names(b_p_apriori)[i]]]<-as.factor(b_p_apriori[[names(b_p_apriori)[i]]])
}
b_p_sparse_matrix_1<-as(b_p_apriori,"transactions")
```

## Begin Searching 
 
  Start search frequent items using apriori method. Set paramaeter support=0.06, confidence=0.9, minlen=8. Sort the rules by their lift values and the show top 4 of them, which with a lift of more than 7.

```{r}
library(arules)
library(arulesViz)


rules<-apriori(b_p_sparse_matrix_1,parameter = list(support=0.06,confidence=0.9,minlen=6,maxlen=12),control = list(verbose=T))

rules<-sort(rules,by="lift")
plot(rules)
plot(rules[1:10],method = "graph")
inspect(rules[1:10])
```
  From the scatter plot above, most of the rules are of high value with a lfit of more than 4. We inspect the 10 rules with the highest lift. As shown in the rules, a building permit type 8(otc alterations) with existing and proposed construction type of 5(wood frame) are likely to remian its original use as an office building or 2 family dwelling. And a building with type 8 permission, an existing construction of type 1 and an used as an office is usually located in financial district, just as we expect. 
  
## Some More Exploration
### About Street Suffix
  Since the item "Street Suffix" once shows up as one of the rhs of the rules, it makes me wonder whether the suffix of a street is somewhat a result of the kind of buildings on it. So I run the following script in order to look for all rules with a rhl relating to the suffix "St", "Av" and "Wy", three most common used suffix. 

```{r}
rules_st<-apriori(b_p_sparse_matrix_1,parameter = list(support=0.06,confidence=0.9,minlen=2,maxlen=13),appearance=list(rhs=c("Street.Suffix=St","Street.Suffix=Av","Street.Suffix=Wy"),default="lhs"))
rules_st<-sort(rules_st,by="lift")
inspect(rules_st[1:10])
```
  The ruels found are all of little value(lift close to 1), suggest that there is no relation with the street suffix and the building type on the street.
  
### Finding the specific area occupied by buildings of a certain type of use.
  It's common that some certain types of buildings concentrate in a specific area in a city. The following script use "food/beverage hndlng" as an example to explore this relationship.
  From the first rule below we know that "Tendorloin" is the place of food industry.
```{r}
rules_food<-apriori(b_p_sparse_matrix_1,parameter = list(support=0.001,confidence=0.9,minlen=3,maxlen=12))
rules_food<-subset(rules_food,items %in% "Existing.Use=food/beverage hndlng")
rules_food<-sort(rules_food,by="lift")

inspect(rules_food[1:10])
```
  We can also use this method in another way to find out the main kind of building in a certain area. Take "Castro/Upper Market" as an example.
```{r}
rules_Castro<-apriori(b_p_sparse_matrix_1,parameter = list(support=0.005,confidence=0.7,minlen=8,maxlen=12))
rules_Castro<-subset(rules_Castro,items %in% "Neighborhoods...Analysis.Boundaries=Castro/Upper Market")
rules_Castro<-sort(rules_Castro,by="lift")

inspect(rules_Castro[1:10])
```

